Contention management for Cloud RAN over an optical ring

### 2018-12-13 ISCIS/article.tex
merge

  \begin{figure}[h!]
       \begin{minipage}[b]{0.5\linewidth}
        \begin{center}
      \includegraphics[scale=0.7]{containers}

      \end{center} 
  \end{minipage}
    \begin{minipage}[b]{0.5\linewidth}
        \begin{center}
      \includegraphics[scale=0.7]{containers2}

      \end{center} 
  \end{minipage}

     \caption{Behavior of the containers on the ring.}\label{fig:containers}

  \end{figure}

@@

We now present an algorithm to determine an assignment of the $m_i$, using the method of Prop.\ref{prop:assign} to set the offset at the same positions. We propose three variations to optimize the latency of the BE traffic, by spacing as well as possible the free containers in a period.

@@

      \includegraphics[scale=0.55]{repart0}
     \caption{Packing.}\label{fig:packing}

@@

      \includegraphics[scale=0.55]{repart1}
     \caption{Balancing inside the slot.}\label{fig:packing}

\end{center}
  \end{figure}
\paragraph{Balancing inside the period}

It is possible that there are no unused position as it happens with the parameters of the N-GREEN ring given in Fig.~\ref{fig:params}: $ET = \frac{P}{2}$, $F = 10$ and $n = 5$. Any assignment has exactly one  BBU or RRH at each position. If all the RRHs start to emit in the first slot, then during $ET$ there will be no free containers anywhere on the ring, inducing a huge latency for the BE traffic. 
To mitigate this problem, in a period, the time with free containers in each position must be uniformly distributed over the period as shown in Fig.~\ref{fig:repart2}.
\begin{figure}[h!]
\begin{center}

      \includegraphics[scale=0.55]{repart2}
     \caption{Balancing inside the period.}\label{fig:packing}

\end{center}
  \end{figure}  
  \paragraph{Experimental evaluation}

>>>>

@@

We now present an algorithm using reservation as in Prop.\ref{prop:assign} to set the offsets at the same positions.
In the naive version of the algorithm, we put each RRH in an aribtrary position, for instance one RRH by position.
 We then propose three ideas to optimize the latency of the BE traffic, by spacing as well as possible the free containers in a period.

@@

@@

\paragraph{Balancing inside the period}

It is possible that there are no unused position as it happens with the parameters of the N-GREEN ring given in Fig.~\ref{fig:params}: $ET = \frac{P}{2}$, $F = 10$ and $n = 5$. Any assignment has exactly one  BBU or RRH at each position. If all the RRHs start to emit in the first slot, then during $ET$ there will be no free containers anywhere on the ring, inducing a huge latency for the BE traffic. 
To mitigate this problem, in a period, the time with free containers in each position must be uniformly distributed over the period as shown in Fig.~\ref{fig:repart2}.

     \begin{minipage}[b]{0.5\linewidth}
        \begin{center}
      \includegraphics[scale=0.55]{repart2}

      \captionof{figure}{Repartition in the slot}    \label{fig:repart1}
      \end{center} 
  \end{minipage}
    \begin{minipage}[b]{0.5\linewidth}
        \begin{center}
      \includegraphics[scale=0.55]{repart1}

      \captionof{figure}{Repartition in the period}    \label{fig:repart2}
      \end{center} 
  \end{minipage}

  \paragraph{Experimental evaluation}
